### 2022-01-23 manuscripts/owp_fim4_2022/dependencies/trackchanges-0.7.0/testing/testing_edit.tex
minor changes

\emph{Cut to a courtroom. Severe atmosphere.}

@@

Michael Norman Randall, you have been found guilty of the murder of Arthur Reginald Webster, Charles Patrick Trumpington, Marcel Agnes Bernstein, Lewis Anona Rudd, John Malcolm Kerr, Nigel Sinclair Robinson, Norman Arthur Potter, Felicity Jayne Stone, Jean-Paul Reynard, Rachel Shirley Donaldson, Stephen Jay Greenblatt, Karl-Heinz Mullet, Belinda Anne Ventham, Juan-Carlos Fernandez, Thor Olaf Stensgaard, Lord Kimberley of Pretoria, Lady Kimberley of Pretoria, The Right Honourable Nigel Warmsly Kimberley, Robert Henry Noonan and Felix James Bennett, on or about the morning of the 19th December 1972. Have you anything to say before I pass sentence?

@@

Yes, sir. I'm very sorry.

@@

\noindent\\ Second Policeman:

@@

It was plain sailing apart from the arrest.

@@

@@

Oh thank you. (very chuffed)

@@

No, no, it was very interesting.

>>>>

\annote[novi]{\emph{Cut to a courtroom. Severe atmosphere.}}{In the Flying Circus there is never a ``severe'' atmosphere.}

@@

Michael Norman Randall, you have been found guilty of the murder of Arthur Reginald Webster, Charles Patrick Trumpington, Marcel Agnes Bernstein, Lewis Anona Rudd, John Malcolm Kerr, Nigel Sinclair Robinson, \change[ym]{Norman Arthur Potter}{Harry Potter}, \add[novi]{Thing 1 \& Thing 2, }\add[ym]{Humpty Dumpty, }\add[three]{Superman, }\add[quatro]{Cold Fusion, }\add[pyat]{The Lorax, }\add[one more]{Mr. T, }\add{The Dread Pirate Roberts, }Felicity Jayne Stone, Jean-Paul Reynard, Rachel Shirley Donaldson, Stephen Jay Greenblatt, Karl-Heinz Mullet, Belinda Anne Ventham, Juan-Carlos Fernandez, Thor Olaf Stensgaard, Lord Kimberley of Pretoria\note{Isn't Pretoria in South Africa?}, \remove{Lady Kimberley of Pretoria, }The Right Honourable Nigel Warmsly Kimberley, Robert Henry Noonan\add[novi]{, Your Mom} and Felix James Bennett, on or about the morning of the 19th December 1972\refneeded[novi]{}. Have you anything to say before I pass sentence?

@@

\annote[ym]{Yes, sir. I'm very sorry.}{That was short.}

@@

\noindent\\ \annote{Second Policeman:

@@

It was plain sailing apart from the arrest.}{That could have been left out.}

@@

\remove[ym]{\noindent\\ Counsel:

@@

Oh thank you. (very chuffed)}

@@

No, no, it was very \change{interesting}{fascinating}.

### 2022-01-23 manuscripts/owp_fim4_2022/sections/materials_and_methods.tex
minor changes

FEMA & Cross-Sections & HEC-RAS 1-D cross-sections used for modeling in BLE datasets. Includes discharges for 1\% and 0.2\% recurrence interval events. \\

@@

FEMA & Flood Inundation Extents & Inundation depths produced by InFRM BLE HEC-RAS 1D for 1\% and 0.2\% recurrence interval events. \\

>>>>

InFRM & Cross-Sections & HEC-RAS 1-D cross-sections used for modeling in BLE datasets. Includes discharges for 1\% and 0.2\% recurrence interval events. \\

@@

InFRM & Flood Inundation Extents & Inundation depths produced by InFRM BLE HEC-RAS 1D for 1\% and 0.2\% recurrence interval events. \\
